\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-14 manuscript.Rmd
preliminary participants section

@@

## Procedure
### Development of the Scale
1. How the items were generated
2. How the literature was reviewed to identify construct adequacy of the items.
3. Discuss the expert panel review process to assess content validity

@@

## Procedure
Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA)  to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]

### Data Collection
Timeline of data collection, 
ethical approval
mode of data collection
how consent was recorded.

@@

We used R (version 4.1.0), including several R packages, for our analyses. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (pa), a factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by the minimum residuals extraction method as well. We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.  Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999]. Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]). Multivariate skew was  = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30. The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`. And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.

@@

Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary). Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018a]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.

@@

\newpage
# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

>>>>

```{r prepareDescTable, include=FALSE}

listdescVars <- colnames(descriptives.data[c(1:3,5:7)])

#seperating naming and  reducing data for descriptive Table 
desctable.data <- select(descriptives.data, c(listdescVars,
                          IncludedInCFA))

#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
 "2. CFA Sample"
desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
 "1. EFA Sample"

# recode the Gender factor so it will only show "Gender Diverse" in the summary table
desctable.data$slypos_demographics_gender.factor <-
  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
         "Yes"= "No")

# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
desctable.data %>%
  tbl_summary(
    by = IncludedInCFA,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
                 slypos_demographics_language.factor ~ "Native English Speaker",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>%
as_kable(format = 'pipe') -> desc_kable #save it as a kable

```{r DescTabPrint, results='asis'}

desc_kable

Table 1 summarizes the demographic characteristics of the online survey participants. Anonymous online questionnaire responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. XX participants were excluded from analysis due to not passing at least one of the "attention check" items. The EFA sample included participants filling out the questionnaire from XX.XX.XXXX to YY.YY.YYYY, whereas participants who filled out the questionnaire from ZZ.ZZ.ZZZZ to 03.09.2021 were included in the CFA analysis. Participants reported filling out the online survey from a diverse range of geographic locations. The four most common geographic locations included:

@@

## Procedure

### Development of the Scale

1.  How the items were generated
2.  How the literature was reviewed to identify construct adequacy of the items.
3.  Discuss the expert panel review process to assess content validity

@@

## Procedure

Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]

### Data Collection

Timeline of data collection, ethical approval mode of data collection how consent was recorded.

@@

We used R (version 4.1.0), including several R packages, for our analyses. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (pa), a factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by the minimum residuals extraction method as well. We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;

@@

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999]. Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]). Multivariate skew was = `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p \<0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018]. Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001] indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30. The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`. And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.

@@

Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (\<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary). Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018a]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.

@@

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

\endgroup
